---
title: "Check blanks"
author: "Brett Longworth"
date: "2021-06-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Check for issue where `fm_corr` is different than the LBC Fm calculated using `norm_ratio` and `lg_blk_fm`. These values from the DB and the function below should be what SNICSer uses to produce `fm_corr`. Differences in stored values may be caused by editing flagging of standards after blank correction, before writing to the DB.

```{r, message = FALSE}
library(amstools)
library(tidyverse)
library(dbplyr)
library(knitr)

options(list(digits = 4, scipen = 4))
```

Create database connection and look at a few lines from snics_results.

```{r}
db <- conNOSAMS()
df <- tbl(db, "snics_results")

df %>% 
  filter(runtime > '2020-01-01') %>% 
  arrange(runtime) %>% 
  head()
```

Find samples where `fm_corr` does not match Fm corrected using `norm_ratio` and `lg_blk_fm` for that sample.

```{r}
df %>% 
  select(wheel, wheel_pos, sample_type, 
         runtime, norm_ratio, lg_blk_fm, fm_corr) %>% 
  mutate(norm_fm_r = norm_ratio - lg_blk_fm * (1.0398 - norm_ratio) / 1.0398,
         diff = norm_fm_r - fm_corr) %>%  
  filter(runtime > '2020-01-01' & 
         lg_blk_fm > 0 &
         abs(diff) > 0.000001 &
           wheel == "CFAMS060221") %>% 
  arrange(runtime)
```

Wheels where this is happening.

```{r}
df %>% 
  select(wheel, wheel_pos, sample_type, 
         runtime, analyst1, analyst2, 
         norm_ratio, lg_blk_fm, fm_corr) %>% 
  mutate(norm_fm_r = norm_ratio - lg_blk_fm * (1.0398 - norm_ratio) / 1.0398,
         diff = norm_fm_r - fm_corr) %>% 
  filter(runtime > '2020-01-01' & 
         lg_blk_fm > 0 &
         abs(diff) > 0.0000001,
         sample_type == "S") %>% 
  group_by(wheel) %>% 
  filter(mean(norm_ratio) < 1.05) %>% 
  summarize(runtime = min(runtime, na.rm = TRUE),
            diff_mean = mean(diff, na.rm = TRUE)) %>% 
  arrange(runtime) %>% 
  kable()

```


Checking issue with std ratio in blank correction..

```{r}
cf62 <- df %>% 
  select(wheel, wheel_pos, sample_type, 
         runtime, norm_ratio, lg_blk_fm, fm_corr) %>% 
  mutate(norm_fm_r = norm_ratio - lg_blk_fm * (1.0398 - norm_ratio) / 1.0398,
         diff = norm_fm_r - fm_corr) %>%  
  filter(runtime > '2020-01-01' & 
         lg_blk_fm > 0 &
         abs(diff) > 0.000001 &
           wheel == "CFAMS060221" &
           wheel_pos > 83) %>% 
  arrange(wheel_pos)

stdrat <- cf62 %>% 
  filter(sample_type == "S") %>% 
  pull(norm_ratio) %>% 
  mean()

cf62 %>% 
  mutate(cor_norm_fm_r = norm_ratio - lg_blk_fm *(stdrat - norm_ratio)/stdrat)
```